A graph-based approach for interactive evolutionary computation

### 2017-01-17 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Intro cont
Planned Sections

  \item Many kinds of relationships between users and individuals,
  can be expressed using common actions found in social networks;
  for instance share, like, or add to collection.

  \item The same graph can be used to have a user model.
\end{enumerate}

\subsection{Subsection Heading Here}
Subsection text here.,
\cite{Sims:1991}

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

>>>>

  \item Many kinds of relationships between users and individuals,
  can be expressed using common actions found in social networks;
  for instance share, like, or add to collection. [ cite Activity Streams 2.0
  syntax (https://www.w3.org/TR/activitystreams-vocabulary)]

  \item The same graph can be used to immplement a user model, or it can
  be extracted from a user\'s public profile.

\end{enumerate}

In this work..

The remainder of this paper proceeds as follows.
Section \ref{sec:interactive} presents related work on the topic 
of Interactive Evolution data models.
Then, Section \ref{sec:evospace-i} presents the computational platform on which the main proposal of this work is developed. The proposed graph model is presented in Section \ref{sec:graph}.
The experimental work and results are presented in Section \ref{sec:experiments}.
Finally, a concluding remarks are provided in Section \ref{sec:conclusions}.

\subsection{Related Work}
\label{sec:interactive}

\subsection{EvoSpace-Interactive}
\label{sec:evospace-i}

\subsection{IEC Graph based model}
\label{sec:graph}

\subsection{Experiments}
\label{sec:experiments}

\subsection{Conclusions}
\label{sec:conclusions}
